Efficient Handling of String-Number Conversion

### 2019-11-23 draft.tex
tiny fix in orange

\changed{
The correctness of the entire construction of $\underf \dr {\insc}$ is expressed by  Theorem~\ref{theorem:correct}. 
It uses the decoding function $\decode \dr$ parameterized by the domain restriction $\dr$. 
The function takes as an argument an $\dr$-encoding of a string constraint, an interpretation $I_e \cup I_z$ consisting of a \emph{many-word encoding} $I_e: V_\dr\cup\#V_\dr\rightarrow \nat$ and an integer variables $I_z$. 
Intuitively, the many-word encoding $I_e$ contains for each $x\in X$ a $\dr(x)$-encoding of its value. 
The function then returns the set of string constraint interpretations 
$\decode  \dr (I_e\cup I_z) \defeq \{I_s \cup I_z \mid \forall x\in X: I_s(x) = \decode {\dr(x)} ((I_e)_{V_{\dr(x)}\cup \#V_{\dr(x)}})\}$.
The condition says that each string variable $x$ is interpreted as the ${\dr(x)}$-decoding of the word encoding $(I_e)_{V_{\dr(x)}\cup \#V_{\dr(x)}}$.
%We define the output of $\decode  \dr (I_e\cup I_z)$ as a set so that \emph{invalid word encodings}, i.e. those do not corresponds to possible word encodings from PFAs, are mapped to empty sets and valid ones are mapped to singleton sets.
We also define the $\dr$-encoding function as the counterpart of $\dr$-decoding,  
%
namely, for a model $I_s \cup I_z$ of a string constraint,  
we let $\encode \dr (I_s \cup I_z) =\{I_e\cup I_z\mid \decode \dr (I_e\cup I_z) = I_s \cup I_z \}$.
We lift $\decode \dr$ and $\encode \dr$ to sets of interpretations in the standard manner.
}

>>>>

\changed{
The correctness of the entire construction of $\underf \dr {\insc}$ is expressed by  Theorem~\ref{theorem:correct}. 
It uses the decoding function $\decode \dr$ parameterized by the domain restriction $\dr$. 
The function takes as an argument an $\dr$-encoding of a string constraint, an interpretation $I_e \cup I_z$ consisting of a \emph{many-word encoding} $I_e: V_\dr\cup\#V_\dr\rightarrow \nat$ and an integer variable interpretation $I_z$. 
Intuitively, the many-word encoding $I_e$ contains for each $x\in X$ a $\dr(x)$-encoding of its value. 
The function then returns the set of string constraint interpretations 
$\decode  \dr (I_e\cup I_z) \defeq \{I_s \cup I_z \mid \forall x\in X: I_s(x) = \decode {\dr(x)} ((I_e)_{V_{\dr(x)}\cup \#V_{\dr(x)}})\}$.
The condition says that each string variable $x$ is interpreted as the ${\dr(x)}$-decoding of the word encoding $(I_e)_{V_{\dr(x)}\cup \#V_{\dr(x)}}$.
%We define the output of $\decode  \dr (I_e\cup I_z)$ as a set so that \emph{invalid word encodings}, i.e. those do not corresponds to possible word encodings from PFAs, are mapped to empty sets and valid ones are mapped to singleton sets.
We also define the $\dr$-encoding function as the counterpart of $\dr$-decoding,  
%
namely, for a model $I_s \cup I_z$ of a string constraint,  
we let $\encode \dr (I_s \cup I_z) =\{I_e\cup I_z\mid \decode \dr (I_e\cup I_z) = I_s \cup I_z \}$.
We lift $\decode \dr$ and $\encode \dr$ to sets of interpretations in the standard manner.
}
